---
title: "README"
author: "Peter Meißner"
date: "Wednesday, September 24, 2014"
output:
  html_document:
    keep_md: yes
---


# diffr 
A package for measuring change between different versions of text

## Description


A package for measuring change between different versions of text by automatically
or semi-automatically aligning text lines and measuring the change. It works kind of like diff
or version control systems but focuses on **measuring** the **change** in contrast to focusing on
solid version control. Furthermore, the package allows for (possibly user made) text cleaning
functions that are applied before comparison. Another feature is the semi-automatic alignment
that allows for fast computer decissions on clear alignments of 100% matches and 0% matches
while asking for human input on more complex decissions.
  

## Installation


    # require(devtools)
    # install_github("petermeissner/diffr")
    # require(diffr)

    
## Links

- http://www.polver.uni-konstanz.de/sieberer/forschung/


## Example Usage

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 160)
```

```{r}

    library(diffr)

    res <- diffr(example_A1_split, example_A2_split, 
                 clean="none", dist="levenwords", sortDF=0)

    names(res)
    
    # total difference between both texts:
    sum(res$alignment_df$dist)

    # alignment of texts
    head(res$alignment_df)

    # alignment of texts with texts
    data.frame( lnr1  = res$alignment_df$lnr1, 
                lnr2  = res$alignment_df$lnr2, 
                text1 = res$text1_orig[res$alignment_df$lnr1] ,
                text2 = res$text2_orig[res$alignment_df$lnr2] ,
                dist  = res$alignment_df$distance
         )
```
    
    

    
    
    
    
    
    
    
    
    
    
