---
title: "README"
output:
  html_document:
    keep_md: yes
---


# diffr 
A package for measuring change between different versions of text

## Description


A package for measuring change between different versions of text by automatically
or semi-automatically aligning text lines and measuring the change. It works kind of like diff or version control systems but focuses on **measuring** the **change** in contrast to focusing on solid version control. Furthermore, the package allows for (possibly user made) text cleaning functions that are applied before comparison. Another feature is the semi-automatic alignment that allows for fast computer decissions on clear alignments of 100% matches and 0% matches while asking for human input on more complex decissions.
  

## Installation

```{r, eval=FALSE}
    devtools::install_github("petermeissner/diffr")
    require(diffr)
```
    
## Links

- http://www.polver.uni-konstanz.de/sieberer/forschung/
- http://link.springer.com/article/10.1007%2Fs12286-014-0216-7


## Example Usage

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 160)
```

```{r, fig.asp=1.5}
    require(diffr)

    res <- diffr(example_A1_split, example_A2_split, 
                 clean="none", dist="levenwords", sortDF=0)

    names(res)
    
    # total difference between both texts:
    sum(res$alignment_df$dist, na.rm=T)

    # alignment of texts
    head(res$alignment_df)

    # alignment of texts with texts
    res$print
    
    # graphical overview
    plot(res)
```
    
   

    
    
    
    
    
    
    
    
    
    
